Predicting Political Support in the United States

### 2024-03-17 output/paper.qmd
Try to update formatting

Although there seems to be a strong correlation between if a voter identifies as an other gender to supporting Biden, and a strong correlation between if a voter identifies as an other race to supporting Biden, but these must be considered carefully as within the sample (with seed 302), only 5 and 1 voters identified in those categories respectively. There were various other demographics in the dataset that had relatively small sample sizes, such as: `race` where non Black, White, or Hispanic respondents made up a small portion of the sample, or non Catholic, Protestant, or Atheist respondents in `religion`. To get a more accurate reading in regards to these features, it would be necessary to train a model which includes a larger sample size of these demographics or to find a way to account for these values while still making use of them. This was a scenario that one may expect to see as there can always be underrepresented demographics in a 60000 respondent sized sample. This is a big limitation to our models, and is something that should be considered when interpreting the results.

@@

# Appendix {.unnumbered}

>>>>

Although there seems to be a strong correlation between if a voter identifies as an other gender to supporting Biden, and a strong correlation between if a voter identifies as an other race to supporting Biden as suggested by the 90% confidence interval for each shown in @fig-confother, but these must be considered carefully as within the sample (with seed 302), only 5 and 1 voters identified in those categories respectively. There were various other demographics in the dataset that had relatively small sample sizes, such as: `race` where non Black, White, or Hispanic respondents made up a small portion of the sample, or non Catholic, Protestant, or Atheist respondents in `religion`. To get a more accurate reading in regards to these features, it would be necessary to train a model which includes a larger sample size of these demographics or to find a way to account for these values while still making use of them. This was a scenario that one may expect to see as there can always be underrepresented demographics in a 60000 respondent sized sample. This is a big limitation to our models, and is something that should be considered when interpreting the results.

@@

\newpage
# Appendix {.unnumbered}
